|

### 2019-03-27 rap/article.Rmd
add

On 11 September 1973, Army General Augusto Pinochet led a coup against Chile's socialist President Salvador Allende. The coup marked the beginning of a seventeen-year military dictatorship that undertook a rapid liberalisation of the Chilean economy while perpetrating systematic violence against the opposition [@meadowcroft2014hayek; @valdes1995pinochet]. The extent of the human rights abuses during the Pinochet regime remains unknown. However, in 1991 then-President Patricio Aylwin created a commission to investigate the most serious violations that happened during the military period. The Report of the Chilean National Commission on Truth and Reconciliation [-@report1991], or the Rettig Report[^rettig], records over 2,000 cases of murders and disappearances. In most cases, there is some detail as to the personal characteristics of the victim, and where and when they died or disappeared, and in many cases there is information as to how that person died. The Report proved a major milestone in the pursuit of justice for the victims of the regime.

@@

>>>>

On 11 September 1973, Army General Augusto Pinochet led a coup against Chile's socialist President Salvador Allende. The coup marked the beginning of a seventeen-year military dictatorship which combined large-scale political repression with rapid economic liberalisation [@meadowcroft2014hayek; @valdes1995pinochet]. In 1991, after the transition to democracy, then-President Patricio Aylwin created a commission to investigate human rights abuses in the Pinochet regime. The Report of the Chilean National Commission on Truth and Reconciliation [-@report1991], also known as the Rettig Report[^rettig], records over 2,000 cases of murders and disappearances from 1973 to 1990. In most cases, there are some details as to the personal characteristics of the victim, and where and when they died or disappeared. Despite its omissions[^omissions].

@@

[^omissions]: The Truth and Commission Report investigated only cases of death and disappearances, leaving aside a high number of other serious human rights violations committed by the Pinochet government. For instance, the Report makes no mention of cases of torture or forced exile, which comprise a significant share of the reported violations [@ensalaco1994truth, 660].
